---
title: "Work on Matching"
author: "Barry DeCicco"
date: '2022-07-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(magrittr)
library(sqldf)
library(tidyverse)



```

# Work on Matching

This document covers some features of matching data in R, and unexpected
but logical problems which can happen.


## Create data:

* Monthly Patient Volume.
* Monthly Case Counts, by Level of Care.
  * Delete October's data from Case Counts - there were no cases in that month.


```{r set-up-data}

Volume <-  c("a", "b", "c" ,"d" ,"e", "f", "g", "h", "i", "j" ,"k", "l")
View(Volume)

df1 <- as.data.frame(cbind(Months, Volume))
View(df1)

Case_Count <- c(runif(24,1,99))
View(Case_Count)
df2 <- as.data.frame(cbind(Months, Case_Count))
View(df2)

df2 <- df2 %>% 
  dplyr::filter(!Months == "June")
View(df2)



```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
